---
title: "Barkai Network Analysis Walkthrough"
author: "Anna Redgrave"
date: "2023-01-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objectives

* Delve more in-depth into the rationale behind different parts of the network analysis
* Document all the different iterations of the analysis in one place to avoid repeating mistakes
* Ideally help other people conduct similar analyses

## Useful resources I follow

* WGCNA! All the tutorials: https://horvath.genetics.ucla.edu/html/CoexpressionNetwork/Rpackages/WGCNA/
* Jeremy Miller's WGCNA meta-analysis tutorial: https://horvath.genetics.ucla.edu/html/CoexpressionNetwork/JMiller/ (Miller JA, Horvath S, Geschwind DH. (2010) Divergence of human and mouse brain transcriptome highlights Alzheimer disease pathways. Proc Natl Acad Sci U S A. 2010 Jul 13;107(28):12698-703.)
* DESeq2 vignette: http://bioconductor.org/packages/devel/bioc/vignettes/DESeq2/inst/doc/DESeq2.html


## Data cleaning 
```{r tidyverse openxlsx}

```

## Network construction

```{r}
```

